Stock enhancement undermines ecological stability

### 2022-02-21 rmd/manuscript.Rmd
edit: reference

Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S4-S6**). In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S4 and S5**). This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021]. More importantly, the contrasting community response at different carrying capacities provides deeper insights. One of the core motivations for stock enhancement is to mitigate declining trends of natural resources due to human impacts, such as habitat loss [@chaseEcosystemDecayExacerbates2020]. Ironically, our results suggest that stock enhancement will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.

>>>>

Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S4-S6**). In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S4 and S5**). This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [e.g., @jonesRestorationMauritiusKestrel1995]. More importantly, the contrasting community response at different carrying capacities provides deeper insights. One of the core motivations for stock enhancement is to mitigate declining trends of natural resources due to human impacts, such as habitat loss [@chaseEcosystemDecayExacerbates2020]. Ironically, our results suggest that stock enhancement will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.
